**Accuracy and precision of 16S rRNA gene sequence assignments to OTUs is more important than the stability of OTUs**

### 2015-10-01 Schloss_Cluster_PeerJ_2015.Rmd
Outlining sections and turn off echoing

```{r knitr.settings, eval=TRUE, echo=FALSE, cache=TRUE}
opts_chunk$set("tidy" = TRUE)
opts_chunk$set("echo" = TRUE)
opts_chunk$set("eval" = TRUE)
opts_chunk$set("warning" = FALSE)
opts_chunk$set("cache" = FALSE)

@@

@@

@@

***Roesch Canadian soil dataset***
After obtaining the 16S rRNA gene fragments from GenBank (accessions EF308591-EF361836), we followed the methods outlined by the He study by removing any sequence that contained an ambiguous base, was identified as being a chimera, and fell outside a defined sequence length. Although they reported observing a total of 50,542 sequences that were represented by 13,293 unique sequences, we obtained a total of `r length(scan("data/he/canada_soil.good.unique.pick.redundant.fasta", what="", sep="\n", quiet=T))/2` sequences that were represented by `r length(scan("data/he/canada_soil.good.unique.pick.fasta", what="", sep="\n", quiet=T))/2` unique sequences. Similar to the He study, we randomly sampled, without replacement, 20, 40, 60, and 80% of the sequences from the full data set. The random sampling was repeated 30 times. The order of the sequences in the full dataset was randomly permuted without replacement to generate an additional 30 datasets. For the hierarchical clustering algorithms and to generate a distance matrix, the pairwise distances between sequences were calculated in mothur using the pairwise.seqs command with the default Needleman-Wunsch alignment algorithm and parameters. Execution of the clustering algorithms was performed as described in the original He study using mothur (v.1.37) and QIIME (v.1.9.1) as appropriate.

>>>>

```{r knitr.settings, eval=TRUE, echo=FALSE, cache=TRUE}
opts_chunk$set("tidy" = TRUE)
opts_chunk$set("echo" = FALSE)
opts_chunk$set("eval" = TRUE)
opts_chunk$set("warning" = FALSE)
opts_chunk$set("cache" = FALSE)

@@

* Compare MCC and its variation when using different algorithms
* Address stability
* Quality of algorithms are data-dependent

@@

* MCC for VAGC/VDGC > AGC/DGC
* MCC for VAGC and VDGC are basically the same
* Stability of VAGC/VDGC goes up

@@

***454 FLX-generated Roesch Canadian soil dataset***
After obtaining the 16S rRNA gene fragments from GenBank (accessions EF308591-EF361836), we followed the methods outlined by the He study by removing any sequence that contained an ambiguous base, was identified as being a chimera, and fell outside a defined sequence length. Although they reported observing a total of 50,542 sequences that were represented by 13,293 unique sequences, we obtained a total of `r length(scan("data/he/canada_soil.good.unique.pick.redundant.fasta", what="", sep="\n", quiet=T))/2` sequences that were represented by `r length(scan("data/he/canada_soil.good.unique.pick.fasta", what="", sep="\n", quiet=T))/2` unique sequences. Similar to the He study, we randomly sampled, without replacement, 20, 40, 60, and 80% of the sequences from the full data set. The random sampling was repeated 30 times. The order of the sequences in the full dataset was randomly permuted without replacement to generate an additional 30 datasets. For the hierarchical clustering algorithms and to generate a distance matrix, the pairwise distances between sequences were calculated in mothur using the pairwise.seqs command with the default Needleman-Wunsch alignment algorithm and parameters. Execution of the clustering algorithms was performed as described in the original He study using mothur (v.1.37) and QIIME (v.1.9.1) as appropriate.

***MiSeq-generated Murine gut microbiota dataset***

***Analysis of reference database***
* used gg_13_8 with the 97_otus.fasta as the reference

***Calculation of Matthew's Correlation Coefficient***

-> Available within mothur as the sens.spec command

***Software availability***
QIIME v.1.9.1
mothur v.1.37.0
R v.3.2
Reproducible workflow including this manuscript as a literate programming document is available at https://github.com/SchlossLab/Schloss_Cluster_PeerJ_2015
